Analyzing Coopetition Strategies of Services within Communities

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

>>>>

In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low. For any reason our web services may need to stay in a particular comuunity with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have inceased the membership fee to the high ammount of 5 per run. Web services will need to pay 5 bucks on each iteration of tasks being offered. As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities. As reseults show the random and all compete strategies make webservices bank deplete in no time. However our strategic coopetetive decision making process loses budget in a slower pace.
